Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-30 paper.tex
Updates

\author{Final ordering
  to be discussed: Yongping/Val\'erie,
  Yuhong Yan, Tristan.\\
  Department of Computer Science and Software Engineering, Concordia University, Montreal, Quebec, Canada
}

@@

\begin{itemize}
  \item In MR, no seeking withing the splits.
\end{itemize}

>>>>

\author{Final ordering
  to be discussed: Yongping Gao/Val\'erie Hayot-Sasson,
  Yuhong Yan, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
  {first.last}@concordia.ca
}

@@

\begin{itemize}
\item In MR, no seeking withing the splits.
\item Avoid in-memory copies.
\end{itemize}
